Illustration on my write-up and some issues to address

### 2014-04-25 sequential/latex/ICCAD2014/theory.tex
upload files from laptop linux

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

%packages
\usepackage[linesnumbered, ruled]{algorithm2e}
\RequirePackage{amssymb, mathptm}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage{helvet}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{cases}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{subfig}
\usepackage{comment}

%new format
\newtheorem{Algorithm}{Algorithm}
\newdef{Definition}{Definition}
\newtheorem{Theorem}{Theorem}
\newtheorem{Lemma}{Lemma}
\newdef{Example}{Example}

\begin{document}

\title{Verification of Sequential Galois Field Circuits using Algebraic Geometry
\titlenote{Version 0.3, refined theory part with normal basis, proposed details for designing 2 examples.}}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Xiaojun Sun\\
       \affaddr{University of Utah}\\
       \affaddr{Department of Electrical \& Computer Engineering}\\
       \affaddr{Salt Lake City, USA}\\
       \email{xiaojun.sun@utah.edu}
% 2nd. author
\alignauthor
Priyank Kalla\\
       \affaddr{University of Utah}\\
       \affaddr{Department of Electrical \& Computer Engineering}\\
       \affaddr{Salt Lake City, USA}\\
       \email{kalla@ece.utah.edu}
% 3rd. author
%\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
%one who did all the really hard work.}\\
%       \affaddr{The Th{\o}rv{\"a}ld Group}\\
%       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
%       \affaddr{Hekla, Iceland}\\
%       \email{larst@affiliation.org}
%\and  % use '\and' if you need 'another row' of author names
% 4th. author
%\alignauthor Lawrence P. Leipuner\\
%       \affaddr{Brookhaven Laboratories}\\
%       \affaddr{Brookhaven National Lab}\\
%       \affaddr{P.O. Box 5000}\\
%       \email{lleipuner@researchlabs.org}
% 5th. author
%\alignauthor Sean Fogarty\\
%       \affaddr{NASA Ames Research Center}\\
%       \affaddr{Moffett Field}\\
%       \affaddr{California 94035}\\
%       \email{fogartys@amesres.org}
% 6th. author
%\alignauthor Charles Palmer\\
%       \affaddr{Palmer Research Laboratories}\\
%      \affaddr{8600 Datapoint Drive}\\
%%      \affaddr{San Antonio, Texas 78229}\\
%       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{21 Jan 2014}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
Circuits working in Galois fields are increasingly employed in designs like arithmetic component for Elliptic Curve Cryptography (ECC). 
This work proposes a new method to effectively verify sequential circuits in Galois fields. Algebraic geometry
is introduced to describe circuits behavior and expand the definition of implicit state space traversal. Moreover, Gr\"obner basis
representation is adopted for word-level abstraction on circuit variables to address state explosion problem
with BDDs. Experiments are run with fast Gr\"obner basis computation engine to get competitive results.
\end{abstract}

% A category with the (minimum) three required fields
\category{EDA5.1}{Verification}{Functional, transaction-level, RTL, and gate-level modeling and verification of hardware design}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Verification, Algorithms}

\keywords{Verification, Sequential, Galois Fields, Algebraic Geometry} % NOT required for Proceedings

@@

\begin{figure}
\centering
\psfig{file=./sequential_fig.ps, height=2in, width=3.5in,}
\caption{A typical sequential circuit block view}
\label{fig:sequential}
\end{figure}

A transition function $\Delta$ is a Boolean function about state outputs and all inputs, i.e.
\begin{displaymath}
t_i = \Delta_i(x, s_0, s_1, \dots, s_{k-1})
\end{displaymath}
This constrain could also be written in the form of equation $polynomial = 0$:
\begin{displaymath}
t_i - \Delta_i(x, s_0, s_1, \dots, s_{k-1}) = 0
\end{displaymath}
Solution to this equation is limited within $\{0, 1\}$, which is set of all elements in Galois field $\mathbb{F}_2$.
Furthermore, there exists a one-to-one corresponding relation from Boolean space to Galois field on higher dimension: 
$\mathbb{B}^k \to \mathbb{F}_{2^k}$, which means it is possible to find a set of elements in $\mathbb{F}_{2^k}$ representing
all Boolean values every bit of a bit vector can take. In Galois field, a as \ref{table:booltogalois} shows.
\begin{table}[h]
\centering
\caption{Bit-vector, Exponential and Polynomial representation of
elements in  ${\mathbb{F}}_{2^4} = {\mathbb{F}}_2[x]
\pmod{x^4+x^3+1}$}\label{table:booltogalois}  
\begin{tabular}{|c|c||c|c|} 
\hline
$a_3a_2a_1a_0$ & Polynomial     &$a_3a_2a_1a_0$ & Polynomial  \\
\hline
$0000$        & $0$           & $1000$  &$\alpha^3$\\
\hline
$0001$        & $1$           & $1001$  & $\alpha^3 + 1$\\
\hline
$0010$        &  $\alpha$       & $1010$ & $\alpha^3 + \alpha$  \\
\hline
$0011$        &  $\alpha + 1$   & $1011$ &  $\alpha^3+\alpha+1$\\
\hline
$0100$        &  $\alpha^2$     &  $1100$ &  $\alpha^3 + \alpha^2$\\
\hline
$0101$        & $\alpha^2 + 1$ & $1101$  & $\alpha^3+\alpha^2+1$\\
\hline
$0110$        &  $\alpha^2 + \alpha$ & $1110$ &  $\alpha^3+\alpha^2+\alpha$\\
\hline
$0111$        & $\alpha^2+\alpha+1$ & $1111$ & $\alpha^3+\alpha^2+\alpha+1$\\
\hline
\end{tabular}
\end{table}
A word-level representation on state inputs/outputs can be attained through above correspondence. If the set of 
state inputs $\{s_0, s_1, \dots, s_{k-1}\}$ is denoted by $S$ taking values from $\mathbb{F}_{2^k}$, and
set of outputs $\{t_0, t_1, \dots, t_{k-1}\}$ is denoted by $T$, a word-level transition function can be written as
\begin{displaymath}
T - \Delta(x, S) = 0
\end{displaymath}
If $T - \Delta(x, S)$ is taken as a polynomial $f$, then $f \in \mathbb{F}_{2^k}[x]\ mod\ P(\alpha)$.
\subsection{Gr\"obner Basis Theory}
Gr\"obner basis is used to calculate desired results out of a set of polynomials.
If there exists multiple polynomials $\{f_1, f_2, \dots, f_r\}$ representing constrains on $T, x$ and $S$,
then all polynomials should simultaneously equal to $0$.
\begin{displaymath}
\left\{
  \begin{array}{lc}
  f_1 & = 0\\
  f_2 & = 0\\
  \dots & \ \\
  f_r & = 0
  \end{array} \right.
\end{displaymath}
Solution to these equations is set of values of $(T, x, S)$, which is called \textbf{Variety} of \textbf{ideal}
$I = \langle f_1, f_2, \dots, f_r\rangle $.

@@

\begin{figure}
\centering
\psfig{file=./fsm_fig.ps, height=2in, width=3.5in,}
\caption{Gate-level circuit of combinational logic block of sample FSM}
\label{fig:fsm}
\end{figure}

\begin{figure}
\centering
\psfig{file=./stg_fig.ps, height=2in, width=3.5in,}
\caption{State transition graph of sample FSM}
\label{fig:stg}
\end{figure}

@@

\begin{Theorem}
State variables $S, T$ and sets of states such as $from^i, to^i$ can always be represented as varieties of ideals.
\end{Theorem}
For example in Line 1 of BFS algorithm, assume initial state is $S_3$ in figure \ref{fig:stg}, then corresponding
polynomial $f = \mathcal{F}(S^0) = S^0 - 1 - \alpha$. Consider an ideal $I$ with only one generator $f$, its variety
$V(I) = \{\gamma\ |\ \gamma \in \mathbb{F}_{2^2}, \gamma - 1 - \alpha = 0\}$, which equals to $\{1 + \alpha\}$, the only
valid value $S^0$ can take.

If an ideal contains multiple polynomial specifications, it is necessary to compute Gr\"obner basis with elimination term
order to get one polynomial only on desired variable. In first iteration of Line 4, $to^i$ has multiple specifications,
some of them are transition functions on bit-level:
\begin{displaymath}
\begin{array}{ll}
f_1:& t_0 - (\overline{x}\ and\ \overline{s_0}\ and\ \overline{s_1})\ or\ (s_0\ and\ s_1) \\
f_2:& t_1 - (\overline{s_0}\ and\ x)\ or\ (p\ and\ \overline{s_1})\
\end{array}
\end{displaymath}
And some are bits-to-word definitions fitting polynomial representation of elements in $\mathbb{F}_{2^2}$:
\begin{displaymath}
\begin{array}{ll}
f_3:& S - s_0 - s_1\alpha \\
f_4:& T - t_0 - t_1\alpha
\end{array}
\end{displaymath}
And an polynomial about initial state as mentioned above:
\begin{displaymath}
f_5:\  S - 1 - \alpha
\end{displaymath}
And the rests are vanishing polynomials for every variable, bit-level and word level:
$f_6: x^2 - x; f_7: t_0^2 - t_0; f_8: t_1^2 - t_1; f_9: S^4 - S; f_{10}: s_0^2 - s_0;
f_{11}: s_1^2 - s_1; f_{12}: T^4 - T$

Transition equations here contains some Boolean operators, they can be re-written in terms of operations in Galois fields. 
In $\mathbb{F}_{2}$, let $TRUE = 1, FALSE = 0$, for either element $a$ in this field, considering $0 + 0 = 1 + 1 \equiv 0\ (mod\ 2)$
and $0 + 1 = 1 + 0 \equiv 1\ (mod\ 2)$, the inverse of $a$ is: $\overline{a} = 1 + a$. Similarly all Boolean operators
can be converted within $\mathbb{F}_{2}$, table \ref{table:booltogalois_op} gives part of them and their corresponding
operations in $\mathbb{F}_{2}$:
Also note that there is no specification on initial primary input $x$, in Gr\"obner basis approach this means $x$ is smoothed by
reversely using Shannon's expansion.
\begin{table}
\centering
\caption{Some Boolean operators and corresponding operations in $\mathbb{F}_{2}$}
\label{table:booltogalois_op}
\begin{tabular}{|c|c|} \hline
Boolean operator & operation in $\mathbb{F}_{2}$\\ \hline
$\overline{a}$ & $1 + a$\\ \hline
$a\ and\ b$ & $ab$\\ \hline
$a\ or\ b$ & $a + b + ab$\\ \hline
$a \oplus b$ & $a + b$\\
\hline\end{tabular}
\end{table}
Using elimination term order: $others\ >\ bit$-$level\ inputs/outputs\ >\ S\ >\ T$, compute Gr\"obner basis for ideal
$J = \langle f_1, f_2, \dots, f_{12}\rangle $, the result will include one polynomial $f_T$ contains only variable $T$. In this example,
$f_T = T + 1$. This polynomial equals to $T - 1$ since coefficients of polynomial representation in $\mathbb{F}_{2^2}$ are
limited within $\mathbb{F}_{2}$, where $1 \equiv -1\ (mod\ 2)$. Solution to $f_T = 0$ is $T = 1$, which shows that next
state the machine just reached is $\{S_1(01)\}$.

@@

There are some difficulties with polynomial representation when executing Line 5 and Line 6, it is necessary to explore
how \textbf{Union}, \textbf{Intersection} and \textbf{Complement Set} works in Galois field $\mathbb{F}_{2^k}$. Since
state set variables $from^i, to^i, reached$ all have single polynomial, consider an ideal $I$ with single generator $I = \langle f\rangle $.
Example: assume $I = \langle f\rangle  = \langle T^2 + (1+\alpha)\cdot T+\alpha\rangle $, its variety $V(I) = \{a\ |\ a \in \mathbb{F}_{2^2}\ and\ f(a) = 0\} = \{1, \alpha\}$.
So it is reasonable to specify: union, intersection and complement set mentioned in this paper are all functions on \textbf{varieties}.
To better discuss this problem, introduce following concepts from algebraic geometry:
\begin{Definition}
\label{def:sum}
({\bf Sum of Ideals}) If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then the 
{\bf sum} of $I$ and $J$, denoted by $I + J$, is the set
  \begin{equation}
  I + J = \{f + g\ |\ f \in I \ and\  g \in J\}.
  \end{equation}
Furthermore, if $I = \langle f_1, \dots, f_r\rangle$ and 
$J = \langle g_1, \dots, g_s\rangle$, then 
$I + J = \langle f_1, \dots, f_r, g_1, \dots, g_s\rangle$.
\end{Definition}
\begin{Definition}
\label{def:prod}
({\bf Product of Ideals}) If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then the
{\bf product} of $I$ and $J$, denoted by $I \cdot J$, is defined to be the ideal generated 
by all polynomials $f \cdot g$ where $f \in I$ and $g \in J$. Furthermore, let
$I = \langle f_1, \dots, f_r\rangle$ and $J = \langle g_1, \dots, g_s\rangle$, then
  \begin{equation}
  I \cdot J = \langle f_ig_j\ |\ 1 \leq i \leq r, 1 \leq j \leq s\rangle .
  \end{equation}
\end{Definition}
\begin{Definition}
({\bf Quotient of Ideals}) If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then $I:J$
is the set
  \begin{equation}
  \{f \in k[x_1, \dots, x_n]\ |\ f\cdot g \in I, \forall g \in J\}
  \end{equation}
and is called the {\bf ideal quotient} of $I$ by $J$.
\end{Definition}
These concepts can lead the way to solution by adopting following theorems:
\begin{Theorem}
\label{thm:unionintersect}
If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then ${\bf V}(I + J) = {\bf V}(I)
\bigcap {\bf V}(J)$ and ${\bf V}(I \cdot J) = {\bf V}(I) \bigcup {\bf V}(J)$.
\end{Theorem}
\begin{Theorem}
\label{thm:quotient}
If $I, J$ are ideals with only one generator, then ${\bf V}(I:J) ={\bf V}(I) - {\bf V}(J)$.
\end{Theorem}
Proof to these theorems are referred to (that yellow book?) and (my write-up?).

For varieties intersection $\{1\}\bigcap\{1, \alpha\}$, calculate ideal sum $\langle T+1, T^2 + (1+\alpha)\cdot T+\alpha\rangle  = \langle T+1\rangle $,
its variety is $\{1\}$; for varieties union $\{1,1+\alpha\}\bigcup\{1+\alpha\}$, calculate
ideal product $\langle (T+1+\alpha)\cdot(T^2 + (1+\alpha)\cdot T+\alpha)\rangle  = \langle T^3 + 1\rangle $, its variety
is $\{1, \alpha, 1+\alpha\}$; for complement set of variety $\{1, \alpha\}$, the universal set is
the variety of ideal of vanishing polynomial $V(\langle T^4-T\rangle ) = \{0,1,\alpha,1+\alpha\}$,
so $\overline{V(\langle T^2 + (1+\alpha)\cdot T+\alpha\rangle )} = V(\langle T^4-T\rangle ) - V(\langle T^2 + (1+\alpha)\cdot T+\alpha\rangle )$,
which equals to $V(\langle T^4-T\rangle :\langle T^2 + (1+\alpha)\cdot T+\alpha\rangle ) = V(\langle T^2+(1+\alpha)\cdot T\rangle )$,
the result is $\{0,1+\alpha\}$.

From discussion above, the BFS traversal is completely implemented in Galois field.
If the initial input is $S_3$: $S + 1 + \alpha$, the final return value will be set of
reachable states: $T^4 + T$, i.e. the universal set, $\{S_0, S_1, S_2, S_3\}$.

\subsection{Discussion on Ideal quotient and its generator}
In nature, we are looking varieties as the solutions to specific polynomial $f=0$ WITHIN $\mathbb{F}_{2^n}$, because (affine) varieties are defined
within algebraic closure $k^n$ but we only care about those fall in $\mathbb{F}_{2^n}$.

Theorem \ref{thm:unionintersect} related to DEF. \ref{def:sum} and \ref{def:prod} counts on ideal generators, so there will be no ambiguity on 
new ideals we get from this theorem. It also appeared in Avrunin's CAV paper. The only problem is what ideal quotient operation will give us.
This should be further discussed because the completeness of our algebraic geometry approach will benefit from it. \emph{Singular} has the function of
ideal quotient, so ask from the author maybe another choice.

If we put this conception aside, it is also feasible to define complement set from "solution to 
equation" sense. Assume $f(x) = x + 1 + \alpha = 0$, its solution within $\mathbb{F}_{2^2}$ 
is $\{1+\alpha\}$; meanwhile solutions to vanishing polynomial $v(x) = x^2 + x = 0$ are
$\{0,1,\alpha,1+\alpha\}$. Now compute solutions to $$g(x) = \frac{v(x)}{f(x)} = 0$$,
this requires $v(x) = 0$ and $f(x) \neq 0$, which means the complement set of solution 
to $f(x) = 0$.

Issues to this interpretation: (a) Is $v(x)$ always divisible by $f(x)$? (b) Is $v(x)=0$ and
$f(x) \neq 0$ equivalent with $g(x)=0$ on their solutions? Could $f(x)$ equal to $0$?

>>>>

@@

\begin{figure}[hbt]
\begin{center}
\includegraphics[width=3.5in]{./sequential_fig.eps}
\end{center}
\caption{A typical sequential circuit block view}
\label{fig:sequential}
\end{figure}

A transition function $\Delta$ is a Boolean function about state outputs and all inputs, i.e.
\begin{displaymath}
t_i = \Delta_i(x, s_0, s_1, \dots, s_{k-1})
\end{displaymath}
This constrain could also be written in the form of equation $polynomial = 0$:
\begin{displaymath}
t_i - \Delta_i(x, s_0, s_1, \dots, s_{k-1}) = 0
\end{displaymath}
Solution to this equation is limited within $\{0, 1\}$, which is set of all elements in Galois field $\mathbb{F}_2$.
Furthermore, there exists a one-to-one corresponding relation from Boolean space to Galois field on higher dimension: 
$\mathbb{B}^k \to \mathbb{F}_{2^k}$, which means it is possible to find a set of elements in $\mathbb{F}_{2^k}$ representing
all Boolean values every bit of a bit vector can take. In Galois field, a as \ref{table:booltogalois} shows.
\begin{table}[h]
\centering
\begin{tabular}{|c|c||c|c|} 
\hline
$a_3a_2a_1a_0$ & Polynomial     &$a_3a_2a_1a_0$ & Polynomial  \\
\hline
$0000$        & $0$           & $1000$  &$\alpha^3$\\
\hline
$0001$        & $1$           & $1001$  & $\alpha^3 + 1$\\
\hline
$0010$        &  $\alpha$       & $1010$ & $\alpha^3 + \alpha$  \\
\hline
$0011$        &  $\alpha + 1$   & $1011$ &  $\alpha^3+\alpha+1$\\
\hline
$0100$        &  $\alpha^2$     &  $1100$ &  $\alpha^3 + \alpha^2$\\
\hline
$0101$        & $\alpha^2 + 1$ & $1101$  & $\alpha^3+\alpha^2+1$\\
\hline
$0110$        &  $\alpha^2 + \alpha$ & $1110$ &  $\alpha^3+\alpha^2+\alpha$\\
\hline
$0111$        & $\alpha^2+\alpha+1$ & $1111$ & $\alpha^3+\alpha^2+\alpha+1$\\
\hline
\end{tabular}
\caption{Bit-vector, Exponential and Polynomial representation of
elements in  ${\mathbb{F}}_{2^4} = {\mathbb{F}}_2[x]
\pmod{x^4+x^3+1}$}\label{table:booltogalois}  
\end{table}
A word-level representation on state inputs/outputs can be attained through above correspondence. If the set of 
state inputs $\{s_0, s_1, \dots, s_{k-1}\}$ is denoted by $S$ taking values from $\mathbb{F}_{2^k}$, and
set of outputs $\{t_0, t_1, \dots, t_{k-1}\}$ is denoted by $T$, a word-level transition function can be written as
\begin{displaymath}
T - \Delta(x, S) = 0
\end{displaymath}
If $T - \Delta(x, S)$ is taken as a polynomial $f$, then $f \in \mathbb{F}_{2^k}[x]\ mod\ P(\alpha)$.
\subsection{Gr\"obner Basis Theory}
Gr\"obner basis is used to calculate desired results out of a set of polynomials.
If there exists multiple polynomials $\{f_1, f_2, \dots, f_r\}$ representing constrains on $T, x$ and $S$,
then all polynomials should simultaneously equal to $0$.
\begin{displaymath}
\left\{
  \begin{array}{lc}
  f_1 & = 0\\
  f_2 & = 0\\
  \dots & \ \\
  f_r & = 0
  \end{array} \right.
\end{displaymath}
Solution to these equations is set of values of $(T, x, S)$, which is called \textbf{Variety} of \textbf{ideal}
$I = \langle f_1, f_2, \dots, f_r\rangle $.

@@

\begin{figure}[hbt]
\begin{center}
\includegraphics[scale=0.3]{./stg_fig.ps}
\end{center}
\caption{State transition graph of sample FSM}
\label{fig:stg}
\end{figure}

\begin{figure}[hbt]
\begin{center}
\includegraphics[width=3.5in]{./fsm_fig.eps}
\end{center}
\caption{Gate-level circuit of combinational logic block of sample FSM}
\label{fig:fsm}
\end{figure}

@@

\begin{Theorem}
State variables $S, T$ and sets of states such as $from^i, to^i$ can always be represented as varieties of ideals.
\end{Theorem}
For example in Line 1 of BFS algorithm, assume initial state is $S_0$ in figure \ref{fig:stg}, then corresponding
polynomial $f = \mathcal{F}(S^0) = S^0 - 0$. Consider an ideal $I$ with only one generator $f$, its variety
$V(I) = \{\gamma\ |\ \gamma \in \mathbb{F}_{2^2}, \gamma = 0\}$, which equals to $\{0\}$, the only
valid value $S^0$ can take.

If an ideal contains multiple polynomial specifications, it is necessary to compute Gr\"obner basis with elimination term
order to get one polynomial only on desired variable. In first iteration of Line 4, $to^i$ has multiple specifications,
some of them are transition functions on bit-level:
\begin{displaymath}
\begin{array}{ll}
f_1:& t_0 - (\overline{x}\ and\ \overline{s_0}\ and\ \overline{s_1})\ or\ (s_0\ and\ s_1) \\
f_2:& t_1 - (\overline{s_0}\ and\ x)\ or\ (s_0\ and\ \overline{s_1})\
\end{array}
\end{displaymath}
And some are bits-to-word definitions fitting polynomial representation of elements in $\mathbb{F}_{2^2}$:
\begin{displaymath}
\begin{array}{ll}
f_3:& S - s_0 - s_1\alpha \\
f_4:& T - t_0 - t_1\alpha
\end{array}
\end{displaymath}
And an polynomial about initial state as mentioned above:
\begin{displaymath}
f_5:\  S
\end{displaymath}
And the rests are vanishing polynomials for every variable, bit-level and word level:
$f_6: x^2 - x; f_7: t_0^2 - t_0; f_8: t_1^2 - t_1; f_9: S^4 - S; f_{10}: s_0^2 - s_0;
f_{11}: s_1^2 - s_1; f_{12}: T^4 - T$

Transition equations here contains some Boolean operators, they can be re-written in terms of operations in Galois fields. 
In $\mathbb{F}_{2}$, let $TRUE = 1, FALSE = 0$, for either element $a$ in this field, considering $0 + 0 = 1 + 1 \equiv 0\ (mod\ 2)$
and $0 + 1 = 1 + 0 \equiv 1\ (mod\ 2)$, the inverse of $a$ is: $\overline{a} = 1 + a$. Similarly all Boolean operators
can be converted within $\mathbb{F}_{2}$, table \ref{table:booltogalois_op} gives part of them and their corresponding
operations in $\mathbb{F}_{2}$:
Also note that there is no specification on initial primary input $x$, in Gr\"obner basis approach this means $x$ is smoothed by
reversely using Shannon's expansion.
\begin{table}
\centering
\begin{tabular}{|c|c|} \hline
Boolean operator & operation in $\mathbb{F}_{2}$\\ \hline
$\overline{a}$ & $1 + a$\\ \hline
$a\ and\ b$ & $ab$\\ \hline
$a\ or\ b$ & $a + b + ab$\\ \hline
$a \oplus b$ & $a + b$\\
\hline\end{tabular}
\caption{Some Boolean operators and corresponding operations in $\mathbb{F}_{2}$}
\label{table:booltogalois_op}
\end{table}
Using elimination term order: $intermediate\ bit$-$level\ signals\ >\ bit$-$level\ primary\ inputs/outputs\ >\ S\ >\ T$, compute Gr\"obner basis for ideal
$J = \langle f_1, f_2, \dots, f_{12}\rangle $, the result will include one polynomial $f_T$ contains only variable $T$. In this example,
$f_T = T^2+(\alpha+1)T+\alpha$. This polynomial equals to $T^2-(\alpha+1)T+\alpha$ since coefficients of polynomial representation in $\mathbb{F}_{2^2}$ are
limited within $\mathbb{F}_{2}$, where $x \equiv -x\ (mod\ 2)$ for any element $x$ in the field. Solution to $f_T = 0$ is $T = 1\ or \ T = \alpha$, which shows that next
state the machine just reached is $\{S_1(01), S_2(10)\}$.

Continue to run this traversal algorithm, it will terminates with final reachable states $f_T = T^3+(\alpha+1)T^2+\alpha T$, its solution is $T=0\ or\ T=1\ or\ T=\alpha$,
which shows within total 4 states, state $S_3$ is unreachable from initial state $S_0$.

@@

There are some difficulties with polynomial representation when executing Line 5 and Line 6, it is necessary to explore
how \textbf{Union}, \textbf{Intersection} and \textbf{Complement Set} works in Galois field $\mathbb{F}_{2^k}$. Since
state set variables $from^i, to^i, reached$ all have single polynomial, consider an ideal $I$ with single generator $I = \langle f\rangle $.
Example: assume $I = \langle f\rangle  = \langle T^2 + (1+\alpha)\cdot T+\alpha\rangle $, its variety $V(I) = \{a\ |\ a \in \mathbb{F}_{2^2}\ and\ f(a) = 0\} = \{1, \alpha\}$.

\begin{figure*}[tb]
\begin{center}
\includegraphics[width=\textwidth]{./mySMPO.eps}
\end{center}
\caption{5-bit SMPO}
\label{fig:SMPO}
\end{figure*}

So it is reasonable to specify: union, intersection and complement set mentioned in this paper are all functions on \textbf{varieties}.
To better discuss this problem, introduce following concepts from algebraic geometry:
\begin{Definition}
\label{def:sum}
({\bf Sum of Ideals}) If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then the 
{\bf sum} of $I$ and $J$, denoted by $I + J$, is the set
  \begin{equation}
  I + J = \{f + g\ |\ f \in I \ and\  g \in J\}.
  \end{equation}
Furthermore, if $I = \langle f_1, \dots, f_r\rangle$ and 
$J = \langle g_1, \dots, g_s\rangle$, then 
$I + J = \langle f_1, \dots, f_r, g_1, \dots, g_s\rangle$.
\end{Definition}
\begin{Definition}
\label{def:prod}
({\bf Product of Ideals}) If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then the
{\bf product} of $I$ and $J$, denoted by $I \cdot J$, is defined to be the ideal generated 
by all polynomials $f \cdot g$ where $f \in I$ and $g \in J$. Furthermore, let
$I = \langle f_1, \dots, f_r\rangle$ and $J = \langle g_1, \dots, g_s\rangle$, then
  \begin{equation}
  I \cdot J = \langle f_ig_j\ |\ 1 \leq i \leq r, 1 \leq j \leq s\rangle .
  \end{equation}
\end{Definition}
\begin{Definition}
({\bf Quotient of Ideals}) If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then $I:J$
is the set
  \begin{equation}
  \{f \in k[x_1, \dots, x_n]\ |\ f\cdot g \in I, \forall g \in J\}
  \end{equation}
and is called the {\bf ideal quotient} of $I$ by $J$.
\end{Definition}
These concepts can lead the way to solution by adopting following theorems:
\begin{Theorem}
\label{thm:unionintersect}
If $I$ and $J$ are ideals in $k[x_1, \dots, x_n]$, then ${\bf V}(I + J) = {\bf V}(I)
\bigcap {\bf V}(J)$ and ${\bf V}(I \cdot J) = {\bf V}(I) \bigcup {\bf V}(J)$.
\end{Theorem}
\begin{Theorem}
\label{thm:quotient}
If $I, J$ are ideals with only one generator, then ${\bf V}(I:J) ={\bf V}(I) - {\bf V}(J)$.
\end{Theorem}
Proof to these theorems are referred to (that yellow book?) and (my write-up?).

For varieties intersection $\{1\}\bigcap\{1, \alpha\}$, calculate ideal sum $\langle T+1, T^2 + (1+\alpha)\cdot T+\alpha\rangle  = \langle T+1\rangle $,
its variety is $\{1\}$; for varieties union $\{1,\alpha\}\bigcup\{1+\alpha\}$, calculate
ideal product $\langle (T+1+\alpha)\cdot(T^2 + (1+\alpha)\cdot T+\alpha)\rangle  = \langle T^3 + 1\rangle $, its variety
is $\{1, \alpha, 1+\alpha\}$; for complement set of variety $\{1, \alpha\}$, the universal set is
the variety of ideal of vanishing polynomial $V(\langle T^4-T\rangle ) = \{0,1,\alpha,1+\alpha\}$,
so $\overline{V(\langle T^2 + (1+\alpha)\cdot T+\alpha\rangle )} = V(\langle T^4-T\rangle ) - V(\langle T^2 + (1+\alpha)\cdot T+\alpha\rangle )$,
which equals to $V(\langle T^4-T\rangle :\langle T^2 + (1+\alpha)\cdot T+\alpha\rangle ) = V(\langle T^2+(1+\alpha)\cdot T\rangle )$,
the result is $\{0,1+\alpha\}$.

From discussion above, the BFS traversal is completely implemented in Galois field.
If the initial input is $S_3$: $S + 1 + \alpha$, the final return value will be set of
reachable states: $T^4 + T$, i.e. the universal set, $\{S_0, S_1, S_2, S_3\}$. Modified algorithm could be
written in following interpretation:

\begin{algorithm}[hbt]
\SetAlgoNoLine
 \KwIn{Input-output circuit characteristic polynomial ideal $I_{ckt}$, initial state polynomial $\F(S)$}

  $from^0 = reached = \F(S)$\;
  \Repeat{$new^i == 1$}
  {
  	$i \gets i + 1$\;
	$to^i \gets$GB w/ elimination term order$<I_{ckt}, from^{i-1}>$\;
	$new^i \gets $generator of $<to^i> + (<T^4-T>:<reached>)$\;
  	$reached \gets $generator of $<reached> \cdot <new^i>$\;
	$from^i \gets new^i(S\setminus T)$\;
  }
\Return{$reached$}
\caption {Algebraic Geometry based Traversal Algorithm}\label{alg:modified}
\end{algorithm}

Here $from^i, to^i, new^i$ are all univariate polynomial about $S$ or $T$

\section{Functional Verification}
\subsection{Sequential Galois Arithmetic Multiplier}
Our experiment is to verify the function of a Galois field multiplier after certain clock cycles.
The following design is Sequential Multiplier with Parallel Output (SMPO),
a Normal Basis multiplier based on Massey-Omura algorithm. Inputs and outputs
are all 5-bit word taking value from ${\mathbb F}_{2^5}$. After loading operands
 A and B, setting all output latches to 0 and running for 5 iterations, the 
output should be $R = A\cdot B$ (mod $x^5 + x^2 + 1$).
